Pipit on the Post: Proving Pre- and Post-conditions of Reactive Systems

### 2024-01-18 2024pipit/section/01-Introduction.tex
fix evaluation: ref to kind2 evaluation

\begin{itemize}
  \item we motivate the need to combine manual and automated proofs of reactive systems with a strong specification language (\autoref{s:motivation});
  \item we introduce Pipit, a minimal reactive language that supports rely-guarantee contracts and properties; crucially, proof obligations are annotated with a status --- \emph{valid} or \emph{deferred} --- allowing proofs to be delayed until more is known of the program context (\autoref{s:core});
  \item we describe a \emph{checked semantics} for Pipit, which is parameterised by the property status; after checking deferred properties, programs can be \emph{blessed}, and their properties lifted to valid status (\autoref{s:core:checked});
  \item we describe an encoding of transition systems that can express under-specified rely-guarantee contracts as functions rather than relations; composing functions results in simpler transition systems (\autoref{s:transition});
  \item we identify the invariants and lemmas required to prove that the abstract transition system is an abstraction of the original semantics (\autoref{s:core:causality}, \autoref{s:transition:proof});
  \item similarly, we offer a mechanised proof that the executable transition system preserves the original semantics (\autoref{s:extraction});
  \item finally, we evaluate Pipit by implementing a time-triggered CAN bus driver, which we have partially verified (\autoref{s:evaluation}).
\end{itemize}

>>>>

\begin{itemize}
  \item we motivate the need to combine manual and automated proofs of reactive systems with a strong specification language (\autoref{s:motivation});
  \item we introduce Pipit, a minimal reactive language that supports rely-guarantee contracts and properties; crucially, proof obligations are annotated with a status --- \emph{valid} or \emph{deferred} --- allowing proofs to be delayed until more is known of the program context (\autoref{s:core});
  \item we describe a \emph{checked semantics} for Pipit, which is parameterised by the property status; after checking deferred properties, programs can be \emph{blessed}, and their properties lifted to valid status (\autoref{s:core:checked});
  \item we describe an encoding of transition systems that can express under-specified rely-guarantee contracts as functions rather than relations; composing functions results in simpler transition systems (\autoref{s:transition});
  \item we identify the invariants and lemmas required to prove that the abstract transition system is an abstraction of the original semantics (\autoref{s:core:causality}, \autoref{s:transition:proof});
  \item similarly, we offer a mechanised proof that the executable transition system preserves the original semantics (\autoref{s:extraction});
  \item finally, we evaluate Pipit by implementing the high-level logic of a time-triggered Controller Area Network (CAN) bus driver and verifying an abstract model of a key operation (\autoref{s:evaluation}).
\end{itemize}

### 2024-01-18 2024pipit/section/70-Related.tex
fix evaluation: ref to kind2 evaluation

Verifying the time-triggered CAN driver is trickier, as the restrictions placed on the triggers array --- that triggers are sorted by time-mark, there must be an adequate time-gap between a trigger and its next-enabled, and a trigger's time-mark must be greater-than-or-equal-to its index --- naturally require quantifiers.
As described in \autoref{s:evaluation}, the Kind2 does include experimental array and quantifier support, but in our experiments was limited to verifying small arrays up to 8 or 16 triggers.
Additionally, due to the limitations on top-level array definitions, compiling the program with Lustre~V6 would result in the entire triggers array being copied to the stack each iteration.

>>>>

Verifying the time-triggered CAN driver is trickier, as the restrictions placed on the triggers array --- that triggers are sorted by time-mark, there must be an adequate time-gap between a trigger and its next-enabled, and a trigger's time-mark must be greater-than-or-equal-to its index --- naturally require quantifiers.
As described in \autoref{s:evaluation}, Kind2 does include experimental array and quantifier support, but in our experiments was unable to verify arrays up to the 64 triggers supported by hardware implementations.
Additionally, due to the limitations on top-level array definitions, compiling the program with Lustre~V6 would result in the entire triggers array being copied to the stack each iteration.
